Fixing Vulnerabilities Hinders Maintainability

### 2019-02-11 paper/ICPC19/icpc19.tex
submission version

\begin{enumerate}
	\item Extract relevant data from a dataset containing $716$ security
	refactorings collected from open-source software available on
	GitHub~\cite{Reis:2017:IJSSE}.
	\item A baseline of regular commits was randomly collected from the list of
	projects of the main dataset to evaluate the impact of regular commits on the
	maintainability of open-source software.
  \item Use the Software Improvement Group's\footnote{SIG's website is available
  at \url{https://www.sig.eu/} (Accessed on \today{})} web-based source code analysis
  service \emph{Better Code Hub} (BCH)\footnote{BCH's website is available at
  \url{https://bettercodehub.com/} (Accessed on \today{})} to quantify maintainability
  for both security and regular commits.
\end{enumerate}

%
\begin{figure}[h]
 	\centering 	\includegraphics[width=0.4\textwidth]{figures/methodology.pdf}
 	\caption{Study Methodology}
	\label{fig:met}
\end{figure}
%
\subsection{Dataset}
%
To evaluate the impact of security refactorings on the maintainability of
open-source software, we use a dataset of security flaws which is the outcome of
mining $94$ GitHub projects. Reis and Abreu ($2017$) mined open-source
software aiming at the extraction of real examples --- created by real
developers --- to test and assess the performance of static analysis tools since
using hand-seeded test cases or mutations could lead to misleading assessments
of the capabilities of the tools~\cite{just2014mutants}. The study yielded a
dataset with $716$ test cases for $16$ security patterns. Some of the patterns
are based in the OWASP Top $10$ of $2013$~\cite{oswap:2013} and OWASP Top $10$ of
$2017$~\cite{oswap:2017}. Each test case of the
dataset is a triplet: the commit before the refactoring, the commit responsible
for the refactoring, and the snippets of code that differ from one version to
another (typically, called \textit{diffs}) --- where one can easily review the
code used to fix the security flaw. In this study, we focus on computing the
maintainability of the commits before and after the security refactoring to
evaluate if the impact was positive, negative or none.

@@

The $716$ refactorings in the dataset were run against the BCH toolset to
calculate their maintainability reports. However, there are refactorings
discarded from our study due to limitations of BCH: in particular, lack of
language support and project size. The final dataset used in this paper comprises
$607$ security refactorings labeled as one of the following categories (we
have decided to change the label to \textit{Miscellaneous} of the patterns in
the dataset containing less than $20$ instances):

@@

{
 \bibliographystyle{IEEEtran}
  \bibliography{icpc19}
}

>>>>

\begin{enumerate}
	\item Extract relevant data from a dataset containing $711$ security
	refactorings collected from open-source software available on
	GitHub~\cite{Reis:2017:IJSSE}.
	\item A baseline of regular commits was randomly collected from the list of
	projects of the main dataset to evaluate the impact of regular commits on the
	maintainability of open-source software.
  \item Use the Software Improvement Group's\footnote{SIG's website is available
  at \url{https://www.sig.eu/} (Accessed on \today{})} web-based source code analysis
  service \emph{Better Code Hub} (BCH)\footnote{BCH's website is available at
  \url{https://bettercodehub.com/} (Accessed on \today{})} to quantify maintainability
  for both security and regular commits.
\end{enumerate}

%
\begin{figure}[h]
 	\centering 	\includegraphics[width=0.4\textwidth]{figures/methodology.pdf}
 	\caption{Study Methodology}
	\label{fig:met}
\end{figure}
%
\subsection{Dataset}
%
To evaluate the impact of security refactorings on the maintainability of
open-source software, we use a dataset of security flaws which is the outcome of
mining $94$ GitHub projects. Reis and Abreu ($2017$) mined open-source
software aiming at the extraction of real examples --- created by real
developers --- to test and assess the performance of static analysis tools since
using hand-seeded test cases or mutations could lead to misleading assessments
of the capabilities of the tools~\cite{just2014mutants}. The study yielded a
dataset with $711$ test cases for $16$ security patterns. Some of the patterns
are based in the OWASP Top $10$ of $2013$~\cite{oswap:2013} and OWASP Top $10$ of
$2017$~\cite{oswap:2017}. Each test case of the
dataset is a triplet: the commit before the refactoring, the commit responsible
for the refactoring, and the snippets of code that differ from one version to
another (typically, called \textit{diffs}) --- where one can easily review the
code used to fix the security flaw. In this study, we focus on computing the
maintainability of the commits before and after the security refactoring to
evaluate if the impact was positive, negative or none.

@@

The $711$ refactorings in the dataset were run against the BCH toolset to
calculate their maintainability reports. However, there are refactorings
discarded from our study due to limitations of BCH: in particular, lack of
language support and project size. The final dataset used in this paper comprises
$607$ security refactorings labeled as one of the following categories (we
have decided to change the label to \textit{Miscellaneous} of the patterns in
the dataset containing less than $20$ instances):

@@

{
  \bibliographystyle{unsrt}
  \bibliography{icpc19}
}
